### 2021-10-29 papers/thesis/resubmitted/ch3-disk-slices/disk-slices.tex
Added bstodo notes to indicate changes

As mentioned earlier, we can handle these boundary conditions by incorporating them into the chosen basis OP family. The weight $\Wiii(x,y)$ is of course zero on the boundary of $\Omega$, and in fact any polynomial that vanishes on the boundary will have $\Wiii(x,y)$ as a factor. Hence, any function expanded in the $\bigWiii$ basis will satisfy zero Dirichlet conditions. The same argument can be used to see why any function expanded in the $\bigW^{(2,2,2)}$ basis will satisfy zero Neumann conditions too.

@@

We can tackle the problem as follows. Since $u$ vanishes on the boundary, any polynomial expansion will have $\Wiii(x,y)$ as a factor, and so we can denote the coefficient vector for expansion of $u$ in the $\bigWiii$ OP basis up to degree $N$ by $\vec{u}$, while the coefficient vector for expansion of $f$ in the $\bighdopiii$ OP basis up to degree $N$ we can denote by $\vec{f}$. Since $f$ is known, we can obtain $\vec{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\bseqn{
    \laplacewiii \vec{u} = \vec{f}
}
which can be solved to find $\vec{u}$. In \bsreffig{fig:ds:poisson} we see the solution to the Poisson equation with zero boundary conditions given in \bsrefeqn{eqn:ds:poisson} in the disk-slice $\Omega$. In \bsreffig{fig:ds:poisson} we also show the norms of each block of calculated coefficients of the approximation for four right-hand sides of the Poisson equation with $N = 990$, that is, $491,536$ unknowns. The rate of decay in the coefficients is a proxy for the rate of convergence of the computed solution; as typical of spectral methods, we expect the numerical scheme to converge at the same rate as the coefficients decay. We see that we achieve algebraic convergence for the first three examples, noting that for right hand-sides that vanish at the corners of our disk-slice ($x\in\{\alpha,\beta\}, \: y = \pm \rho(x)$) we observe faster convergence.

>>>>

\bstodoinline{Added the following paragraph to explain BCs better.}As mentioned earlier, we can handle these boundary conditions by incorporating them into the chosen basis OP family. The weight $\Wiii(x,y)$ is of course zero on the boundary of $\Omega$, and in fact any polynomial that vanishes on the boundary will have $\Wiii(x,y)$ as a factor. Hence, any function expanded in the $\bigWiii$ basis will satisfy zero Dirichlet conditions. The same argument can be used to see why any function expanded in the $\bigW^{(2,2,2)}$ basis will satisfy zero Neumann conditions too.

@@

\bstodo{Reworded this paragraph to help make the BC incorporation clearer.}We can tackle the problem as follows. Since $u$ vanishes on the boundary, any polynomial expansion will have $\Wiii(x,y)$ as a factor, and so we can denote the coefficient vector for expansion of $u$ in the $\bigWiii$ OP basis up to degree $N$ by $\vec{u}$, while the coefficient vector for expansion of $f$ in the $\bighdopiii$ OP basis up to degree $N$ we can denote by $\vec{f}$. Since $f$ is known, we can obtain $\vec{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\bseqn{
    \laplacewiii \vec{u} = \vec{f},
}
which can be solved to find $\vec{u}$. In \bsreffig{fig:ds:poisson} we see the solution to the Poisson equation with zero boundary conditions given in \bsrefeqn{eqn:ds:poisson} in the disk-slice $\Omega$. In \bsreffig{fig:ds:poisson} we also show the norms of each block of calculated coefficients of the approximation for four right-hand sides of the Poisson equation with $N = 990$, that is, $491,536$ unknowns. The rate of decay in the coefficients is a proxy for the rate of convergence of the computed solution; as typical of spectral methods, we expect the numerical scheme to converge at the same rate as the coefficients decay. We see that we achieve algebraic convergence for the first three examples, noting that for right hand-sides that vanish at the corners of our disk-slice ($x\in\{\alpha,\beta\}, \: y = \pm \rho(x)$) we observe faster convergence.
